A Java Wrapper For Embarresingly Parallel Problems

### 2013-10-11 paper/paper.tex
More papaer

\begin{abstract}
An embarresingly parallel, also called pleasing parallel, problem is one that 
can easily be broken up into BLANK that do not need to know about one another.
Several problems in the biological sciences are embarrsingly parallel but they
are difficult to rewrite to use multithreading, because they are either poorly
written or too complex. We have written a wrapper, implemented in Java, that
will execute the serial program in several threads. RESULTS SENTENCE. More
statistics, savable configurations and BLANK will be implemented next, in
addition to BLANK.
\end{abstract}

@@

HISTORY OF PARALLELISM

@@

WHAT ARE WE GOING TO DO

SUMMARY OF RESULTS

@@

The KaKs Calculator is not the only embarresingly parallel program that has the
potential to take several days to run on a data set. In fact, there are several
embarresingly parallel programs in the biological sciences. TALK ABOUT OTHER

BLAST, two other things are

PROGRAMS HERE. With this multitude of applications that would benefit from
parallelism, it was obvious that the wrapper program has potential outside of
this project.

@@

Break down the components. Have a UML diagram here first

@@

There are several next steps in the pipeline. In addition to using the
statistics to try to boost speed, adding savable configurations is at the top of
the list. This will allow users to use the same configuration without having to
go through the wizard if they need to redo a run. More extensive unit testing
will be implemented. The ability to chunk multiple pieces of work may be
implemented in order to avoid potential start up costs in the executable. 
Finally, other  pleasing parallel problems will be executed by the wrapper so 
that more potential features will be discovered. MORE

Using Java was a good choice for implementation ease and future implementation
extension by others, but it may not produce the fastest results. Other languages
like Hadoop or blank may have been better due to their parallel nature. DO SOME
RESEARCH. Another approach that could have been taken is one similar to the
bitches in Washington: going to the cloud. WHY THEY WOULD BE BETTER. HOW IT
COULD BE IMPLEMENTED.

@@

\bibitem{aodv}
C. Perkins,  E. Belding-Royer, and  S. Das, ``\emph{Ad hoc On-Demand
Distance Vector (AODV) Routing},'' IETF RFC 3561, July 2003.

>>>>

\begin{abstract}
An embarresingly parallel, also called pleasing parallel, problem is one that 
can easily be broken up into work that does not need to know about one another.
Several problems in the biological sciences are embarrsingly parallel but they
are difficult to rewrite to use multithreading, because they are either poorly
written or too complex. We have written a wrapper, implemented in Java, that
will execute the serial program in several threads. RESULTS SENTENCE. More
statistics, savable configurations and more options will be implemented next, in
addition to better testing and refactored.
\end{abstract}

@@

@@

In this paper, I am going to propose a program that will call the serial
programs on several Java threads. This program will act like the serial
application, reading the input the same and creating the output in the same
format. My wrapper program wraps any embarresingly parallel command line program
that reads from a file, writes to a file and the input can be broken up into
work units by a regular expression. SUMMARY OF RESULTS to end the paragraph.

@@

The KaKs Calculator is not the only embarresingly parallel program that has the
potential to take several days to run on a data set. In fact, there are several
embarresingly parallel programs in the biological sciences. The Basic Local
Alignment Search Tool (BLAST) \cite{BLAST} is a common program used to find
similarities between sequences and then compares them to databases to calculate
the statistical significance. Another program we have been looking at is called
Trinity. Trinity claims to be an efficient way to do de novo reconstruction of
transcriptomes from mRNA sequence data. With this variety of applications that 
would benefit from parallelism, it was obvious that the wrapper program has 
potential outside of this project.

@@

A UML Diagram will go here

@@

There are several next steps in the pipeline. In addition to using the
statistics to try to boost speed, adding savable configurations is at the top of
the list. This will allow users to use the same configuration without having to
go through the wizard if they need to redo a run. More extensive unit testing
will be implemented. The ability to chunk multiple pieces of work may be
implemented in order to avoid potential start up costs in the executable. 
Finally, other pleasing parallel problems will be executed by the wrapper so 
that more potential features will be discovered.

Using Java was a good choice for implementation ease and future implementation
extension by others, but it may not produce the fastest results. Languages
like Hadoop, Clojure or other multithread oriented language may have been better
due to their parallel nature. Another approach that could have been taken is one
similar to the people in Washington: going to the cloud. Using a networked 
solution like MPI or a cloud solution like Amazon instances. (More will go here
when I added in more previous work from others)

@@
